---
title: "vis_1"
author: "Sunny Siddique"
date: "September 27, 2018"
output: html_document
---

Git repo for visualization

```{r}
library(tidyverse)
library(ggridges)
```

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```


Importing rnoaa dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

##Scatter a plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

##Central park

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```


Naming and saving the scatterplot

```{r}
weather_scatter = ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

##More plot options

Add an aesthetic 

```{r}

ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name))

```

Add a geometry

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth(se= FALSE)
```

Add some options

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.4) +
  geom_smooth(se= FALSE)
``` 


Smooth curve for each specific location

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se= FALSE)
``` 


Factting...
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se= FALSE) +
  facet_grid(~ name)
```

A more interesting plot...

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color=name, size = prcp)) + 
  geom_point() + 
  geom_smooth(se=FALSE) +
  facet_grid(~name)
```

line graph

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color=name)) + 
  geom_line()
```

Learning assessment. 

Write a code chain that starts with weather_df; focuses only on Central Park, converts temperatures to Fahrenheit, makes a scatterplot of min vs. max temperature, and overlays a linear regression line (using options in  geom_smooth()).

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>%
  mutate (tmax = tmax+32, tmin = tmin+32) %>% 
  ggplot(aes(x=tmax, y=tmin)) +
  geom_point() +
  geom_smooth()
```


Plotting just the smooth curve
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)
```

```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

Univariate plots...

Histograms

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram()
```

Density plot

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = 0.5)
```

Boxplots
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) +
geom_boxplot()
```

Violin plots
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) +
geom_violin()
```


```{r}
library(ggridges)
ggplot(weather_df, aes(x = tmax, y = name)) +
  geom_density_ridges()

```


Learning Assessment
```{r}
ggplot(weather_df, aes(x = name, y = prcp)) + 
  geom_boxplot()
```

```{r}
ggplot(weather_df, aes(x = name, y = prcp)) + 
  geom_violin()
```

```{r}
weather_df %>% 
  filter(prcp > 0) %>% 
ggplot(aes(x=prcp, fill = name)) +
  geom_density()
```


##Visulaization II

First scatterplot

```{r}
devtools::install_github("thomasp85/patchwork")
```
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5)
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  )
```


Tick marks and labels

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  scale_x_continuous(breaks = c(-15, 0, 15), 
                     labels = c("-15ยบ C", "0", "15"))
```

Transforming axes

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  scale_x_continuous(breaks = c(-15, 0, 15), 
                     labels = c("-15ยบC", "0", "15"),
                     limits = c(-20, 30)) + 
  scale_y_continuous(trans = "sqrt", 
                     position = "right")
```

